Sequence assembly

### 2025-04-11 episodes/sequence-assembly.Rmd
A small correction to seq assembly
A few cosmetic changes and fixing a filepath issue

@@

```bash
skesa <options> 1> results.fasta 2> logfile
```

@@

Hint: https://en.wikipedia.org/wiki/N50,_L50,_and_related_statistics

@@

Write loop over accessions, printing the accession name and running `gt` on each fasta file. Grepping for the information you want. You can grep two different patterns by prefixing each pattern with `-e`. E.g. `grep -e "this" -e "that"` greps this or that.

>>>>

::: discussion

@@

```bash
# Information, don't run that
skesa <options> 1> results.fasta 2> logfile
```
::::::::::::::

@@

Wikipedia is your friend: https://en.wikipedia.org/wiki/N50,_L50,_and_related_statistics

@@

Write a `for` loop over accessions, printing the accession name and running `gt` on each fasta file. Grepping for the information you want. You can grep two different patterns by prefixing each pattern with `-e`. E.g. `grep -e "this" -e "that"` greps this or that.
